Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-21 paperDistance/paper.tex
discussion

\section{Discussion}
Apass HR Diagram looks very different from Rave HR Diagram, MS stars are incorrectly being labeled as giants

Long discussion of dust

Number of gaussians in XD, and the w parameter

\acknowledgments It is a pleasure to thank Andy Casey (Monash) and the
attendees at the Stars Group Meeting at the CCA for comments and
input.

>>>>

\section{Discussion}
What have we achieved and why is it important?

Come back to the assumptions. What happens if we change or violate them?

Long discussion of the noise model. We took serious short-cuts. Call out to Boris.

Long discussion of dust.

Some discussion of possible failure modes. Including very rare kinds of stars.

Number of gaussians in XD, and the w parameter. That we set them heuristically.

\acknowledgments It is a pleasure to thank
  Jo Bovy (Toronto),
  Andy Casey (Monash),
and the attendees at the Stars Group Meeting at the Flatiron Institute
Center for Computational Astrophysics for comments and input.
